Wall and LR Fish

### 2024-03-05 Fish Data Analysis/Walls and LR Turns.qmd
Calculating NN Responses

```{r}
eight_fish_still <- ggplot(eight_fish_data_sum_away %>% filter(Flow == "Still Water"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_line(alpha = 0.25) +
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  #facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

@@

turning_glm_F0LNDN_B <- glm(turn_bool ~ 1,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"),
                         family = binomial)
turning_glm_F0LNDN_W <- glm(turn_bool ~ Wall_Dist,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"),
                         family = binomial)
turning_glm_F0LNDN_F <- glm(turn_bool ~ Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"),
                         family = binomial)
turning_glm_F0LNDN_WF <- glm(turn_bool ~ Wall_Dist*Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"),
                         family = binomial)

@@

turning_glm_F0LYDN_B <- glm(turn_bool ~1,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"),
                         family = binomial)
turning_glm_F0LYDN_W <- glm(turn_bool ~ Wall_Dist,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"),
                         family = binomial)
turning_glm_F0LYDN_F <- glm(turn_bool ~ Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"),
                         family = binomial)
turning_glm_F0LYDN_WF <- glm(turn_bool ~ Wall_Dist*Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"),
                         family = binomial)

@@

turning_glm_F0LNDY_B <- glm(turn_bool ~ 1,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
                         family = binomial)
turning_glm_F0LNDY_W <- glm(turn_bool ~ Wall_Dist,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
                         family = binomial)
turning_glm_F0LNDY_F <- glm(turn_bool ~ Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
                         family = binomial)
turning_glm_F0LNDY_WF <- glm(turn_bool ~ Wall_Dist*Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
                         family = binomial)

@@

turning_glm_F0LYDY_B <- glm(turn_bool ~ 1,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"),
                         family = binomial)
turning_glm_F0LYDY_W <- glm(turn_bool ~ Wall_Dist,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"),
                         family = binomial)
turning_glm_F0LYDY_F <- glm(turn_bool ~ Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"),
                         family = binomial)
turning_glm_F0LYDY_WF <- glm(turn_bool ~ Wall_Dist*Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"),
                         family = binomial)

>>>>

```{r}
eight_fish_still <- ggplot(eight_fish_data_sum_away %>% filter(Flow == "Still Water"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(alpha = 0.25) +
  #geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  #facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

@@

turning_glm_F0LNDN_B <- glm(turn_bool ~ 1,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"),
                         family = binomial)
turning_glm_F0LNDN_W <- glm(turn_bool ~ Left_Wall_Dist,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"),
                         family = binomial)
turning_glm_F0LNDN_F <- glm(turn_bool ~ Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"),
                         family = binomial)
turning_glm_F0LNDN_WF <- glm(turn_bool ~ Left_Wall_Dist*Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"),
                         family = binomial)

@@

turning_glm_F0LYDN_B <- glm(turn_bool ~1,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"),
                         family = binomial)
turning_glm_F0LYDN_W <- glm(turn_bool ~ Left_Wall_Dist,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"),
                         family = binomial)
turning_glm_F0LYDN_F <- glm(turn_bool ~ Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"),
                         family = binomial)
turning_glm_F0LYDN_WF <- glm(turn_bool ~ Left_Wall_Dist*Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"),
                         family = binomial)

@@

turning_glm_F0LNDY_B <- glm(turn_bool ~ 1,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
                         family = binomial)
turning_glm_F0LNDY_W <- glm(turn_bool ~ Left_Wall_Dist,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
                         family = binomial)
turning_glm_F0LNDY_F <- glm(turn_bool ~ Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
                         family = binomial)
turning_glm_F0LNDY_WF <- glm(turn_bool ~ Left_Wall_Dist*Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
                         family = binomial)

@@

turning_glm_F0LYDY_B <- glm(turn_bool ~ 1,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"),
                         family = binomial)
turning_glm_F0LYDY_W <- glm(turn_bool ~ Left_Wall_Dist,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"),
                         family = binomial)
turning_glm_F0LYDY_F <- glm(turn_bool ~ Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"),
                         family = binomial)
turning_glm_F0LYDY_WF <- glm(turn_bool ~ Left_Wall_Dist*Fish_Num_Ratio,
                         data = eight_fish_turning_data %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"),
                         family = binomial)
